Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-03-29 Experiments.tex
Modfied figures

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/weak1.pdf}
    \caption{Weak scalability: average pilot duration, average duration of a
    single AthenaMP execution, and pilot's overhead for different pilot sizes
    (250, 500, 1000 and 2000 worker nodes). Note: the overhead refers to
    the axis on the right and it is expressed in tenths of a second.}
\label{fig:weakScal1a}
\end{figure}

@@

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/weak2.pdf}
    \caption{Weak scalability with multiple generations: average pilot
    duration, average duration of five sequential AthenaMP executions, and
    pilot's overhead for different pilot sizes (256, 512, 1024 and 2048 nodes).
    Note that the overhead refers to the axis on the right and it is expressed
    in tenths of a second.}
\label{fig:weakScal2a}
\end{figure}

@@

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/strong.pdf}
    \caption{Strong scalability:  average pilot duration, average duration of
    sequential AthenaMP executions, and pilot's overhead for different pilot
    sizes (256, 512, 1024 and 2048 nodes). Note that the overhead refers to the
    axis on the right and it is expressed in tenths of a second.}
\label{fig:strongScala}
\end{figure}

>>>>

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/weak1.pdf}
    \caption{Weak scalability: average pilot duration, average duration of a
    single AthenaMP execution, and pilot's overhead for different pilot sizes
    (250, 500, 1000 and 2000 worker nodes). }
\label{fig:weakScal1a}
\end{figure}

@@

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/weak2.pdf}
    \caption{Weak scalability with multiple generations: average pilot
    duration, average duration of five sequential AthenaMP executions, and
    pilot's overhead for different pilot sizes (256, 512, 1024 and 2048 nodes).}
\label{fig:weakScal2a}
\end{figure}

@@

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/strong.pdf}
    \caption{Strong scalability:  average pilot duration, average duration of
    sequential AthenaMP executions, and pilot's overhead for different pilot
    sizes (256, 512, 1024 and 2048 nodes).}
\label{fig:strongScala}
\end{figure}
